PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Chi square tests added for age and ethnicity

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat.raw %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

# Demographics
## Ethnicity_collapsed
### Pie charts
**NEED TO CREATE ETHNICITY_collapsed variable**
```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

@@

```{r ethnicity pie chart biggest group label}
eth_pie_alllabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")  +
    geom_text(aes(y = c(0.5),
                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
             size=5,
             face="bold"
             )

eth_pie_alllabel
```

Pie chart - no labels

```{r ethnicity pie chart no label}
eth_pie_nolabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")

eth_pie_nolabel
```

# Neurological frequencies
** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

@@

```{r neurological frequencies alsfrs.limb_weakness_noticed_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
  count(covid_probable_case_incl_screening, alsfrs.limb_weakness_noticed_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.normal}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.normal)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.normal) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.slow_or_sloppy_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.not_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.not_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.able_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.able_to_grip_pen)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.able_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.unable_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.unable_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.have_you_noticed_any_difficulty_walking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.have_you_noticed_any_difficulty_walking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.do_you_have_any_difficulty_climbing_stairs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("ess"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies ess.felt_excessively_sleepy_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.felt_excessively_sleepy_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_reading}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_and_reading)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_and_reading) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.watching_tv}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.watching_tv)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.watching_tv) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_inactive_in_a_public_place}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_inactive_in_a_public_place) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.break_passenger_car_hour}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.break_passenger_car_hour)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.break_passenger_car_hour) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.afternoon_rest_circumstances_lying}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.afternoon_rest_circumstances_lying) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_talking_to_someone}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_and_talking_to_someone) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_quietly_after_a_lunch_without_alcohol}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.car_minutes_stopped_traffic}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.car_minutes_stopped_traffic) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.insomnia}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.insomnia)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.insomnia) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.narcolepsy}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.narcolepsy)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.narcolepsy) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.rem_sleep_behaviour_disorder}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.rem_sleep_behaviour_disorder) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.restless_legs_syndrome}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.restless_legs_syndrome)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.restless_legs_syndrome) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_apnea}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleep_apnea)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleep_apnea) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_terrors}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleep_terrors)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleep_terrors) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleepwalking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleepwalking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleepwalking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.other}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.other)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.other) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.none}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.none)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.none) %>%
  mutate(Prop = round(n/sum(n), 2))
```

>>>>

## COVID probable diagnosis
```{r COVID probable diagnosis frequencies}
dat.raw %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

# Demographics

## Age
### Proportion tables
```{r age_category per Sample prop per total}
age_category_per_Covid_prop_total <- dat.raw %>%
  count(age_category, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2)) %>% 
  drop_na()

kable(age_category_per_Covid_prop_total)
age_category_per_Covid_prop_total
```

```{r age_category per Sample prop per Sample}
age_category_per_Covid_prop_Covid <- dat.raw %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(age_category, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2)) %>% 
  drop_na()

kable(age_category_per_Covid_prop_Covid)
age_category_per_Covid_prop_Covid
```

### Cross tables
```{r age_category per Sample prop cross table}
age_category_per_Covid_prop_Covid_cross_table <- dat.raw %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(age_category, covid_probable_case_incl_screening) %>%
  drop_na() %>% 
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))

kable(age_category_per_Covid_prop_Covid_cross_table)
age_category_per_Covid_prop_Covid_cross_table
```

### Collapse age categories
```{r Collapse age_category}
dat.raw <- dat.raw %>%
  mutate(age_category_collapsed_numeric =
           case_when(
             age_category_numeric == 1 ~ 0,
             age_category_numeric == 2 ~ 1,
             age_category_numeric == 3 ~ 2,
             age_category_numeric == 4 ~ 3,
             age_category_numeric == 5 ~ 4,
             age_category_numeric == 6 ~ 5,
             age_category_numeric == 7 ~ 6,
             age_category_numeric == 8 ~ 7,
             age_category_numeric == 9 ~ 8,
             age_category_numeric == 10 ~ 8,
             age_category_numeric == 11 ~ 8,
             age_category_numeric == 12 ~ 8,
             age_category_numeric == 13 ~ 8

           )
  )

dat.raw <- dat.raw %>%
  mutate(age_category_collapsed =
           recode_factor(
             age_category_collapsed_numeric,
             `0` = "16-18",
             `1` = "19-25",
             `2` = "26-35",
             `3` = "36-45",
             `4` = "46-55",
             `5` = "56-65",
             `6` = "66-70",
             `7` = "71-75",
             `8` = "76+"
           )
  )

dat.raw %>%
  freq(age_category_collapsed)
```

### Proportion tables
```{r age_category_collapsed per Sample prop per total}
age_category_collapsed_per_Covid_prop_total <- dat.raw %>%
  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2)) %>% 
  drop_na()

kable(age_category_collapsed_per_Covid_prop_total)
age_category_collapsed_per_Covid_prop_total
```

```{r age_category_collapsed per Sample prop per Sample}
age_category_collapsed_per_Covid_prop_Covid <- dat.raw %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2)) %>% 
  drop_na()

kable(age_category_collapsed_per_Covid_prop_Covid)
age_category_collapsed_per_Covid_prop_Covid
```

### Cross tables
```{r age_category_collapsed per Sample prop cross table}
age_category_collapsed_per_Covid_prop_Covid_cross_table <- dat.raw %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
  drop_na() %>% 
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))

kable(age_category_collapsed_per_Covid_prop_Covid_cross_table)
age_category_collapsed_per_Covid_prop_Covid_cross_table
```

### Chi square test
```{r age_category per probable Covid chisquare test}
age_category_per_Covid_chissquare_test <- dat.raw %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
  spread(key = covid_probable_case_incl_screening, value = n) %>%
  select(-age_category_collapsed) %>%
  chisq.test() %>%
  glance()

kable(age_category_per_Covid_chissquare_test)
age_category_per_Covid_chissquare_test
```

## Sex

## Smoking

## BMI

## Key worker status

## Ethnicity_collapsed
### Pie charts
```{r Collapse Ethnicity}
dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0, #European
             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
             Ethnicity_numeric == 4 ~ 3, #African or African British
             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
           )
  )

dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed =
           recode_factor(
             Ethnicity_collapsed_numeric,
             `0` = "European",
             `1` = "Mixed or multiple ethnic origins",
             `2` = "Asian or Asian British",
             `3` = "African or African British",
             `4` = "Other"
           )
  )

dat.raw %>%
  freq(Ethnicity_collapsed)
```

```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(covid_probable_case_incl_screening, Ethnicity_collapsed) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

@@

```{r ethnicity pie chart biggest group label}
Ethnicity_by_Covid_collapsed_count <- Ethnicity_collapsed_prop_Covid %>%
  mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
  group_by(covid_probable_case_incl_screening) %>% 
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = n)
    ) +
  geom_bar(
    aes(fill = covid_probable_case_incl_screening),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity",
    y = "Number of participants",
    fill = "Covid status") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette4
    ) +
  coord_flip()

Ethnicity_by_Covid_collapsed_count

###Chi-square

```{r ethnicity per probable Covid chisquare test}
ethnicity_per_Covid_chissquare_test <- dat.raw %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
  spread(key = covid_probable_case_incl_screening, value = n) %>%
  select(-Ethnicity_collapsed) %>%
  chisq.test() %>%
  glance()

kable(ethnicity_per_Covid_chissquare_test)
ethnicity_per_Covid_chissquare_test
```

# Neurological frequencies

```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

@@

```{r neurological frequencies alsfrs.limb_weakness_noticed_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
  count(covid_test_positive, alsfrs.limb_weakness_noticed_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.normal}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.normal)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.normal) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.slow_or_sloppy_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.not_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.not_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.able_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.able_to_grip_pen)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.able_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.unable_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.unable_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.have_you_noticed_any_difficulty_walking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.have_you_noticed_any_difficulty_walking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.do_you_have_any_difficulty_climbing_stairs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("ess"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies ess.felt_excessively_sleepy_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.felt_excessively_sleepy_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_reading}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_and_reading)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_and_reading) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.watching_tv}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.watching_tv)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.watching_tv) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_inactive_in_a_public_place}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_inactive_in_a_public_place) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.break_passenger_car_hour}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.break_passenger_car_hour)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.break_passenger_car_hour) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.afternoon_rest_circumstances_lying}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.afternoon_rest_circumstances_lying) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_talking_to_someone}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_and_talking_to_someone) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_quietly_after_a_lunch_without_alcohol}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.car_minutes_stopped_traffic}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.car_minutes_stopped_traffic) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.insomnia}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.insomnia)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.insomnia) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.narcolepsy}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.narcolepsy)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.narcolepsy) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.rem_sleep_behaviour_disorder}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.rem_sleep_behaviour_disorder) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.restless_legs_syndrome}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.restless_legs_syndrome)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.restless_legs_syndrome) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_apnea}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleep_apnea)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleep_apnea) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_terrors}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleep_terrors)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleep_terrors) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleepwalking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleepwalking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleepwalking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.other}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.other)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.other) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.none}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.none)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.none) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("midas"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies midas.headaches_suffered_past_month}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.headaches_suffered_past_month)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.headaches_suffered_past_month) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_work_school}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_miss_work_school)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_miss_work_school) %>%
  mutate(Prop = round(n/sum(n), 2))
```
